SI

### 2021-02-22 ms/si.Rmd
Fix landscape mode
needed to make image size slightly smaller to avoid extra blank page

---
title: ""
bibliography: 
  - references.bib
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-plant-research.csl"]
    includes:
      in_header: journal-of-plant-research-si.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
  \usepackage{pdflscape}
  \newcommand{\blandscape}{\begin{landscape}}
  \newcommand{\elandscape}{\end{landscape}}
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

@@

```{r sporophyte-dt-LiCl, fig.height = 7, fig.width = 9.5, fig.cap = ""}
# Get mean times of each cluster of DT test samples for the selected drying salt
licl_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "LiCl", 3)
licl_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "LiCl", 1)

@@

```{r sporophyte-dt-MgNO3, fig.height = 7, fig.width = 9.5, fig.cap = ""}
# Get mean times of each cluster of DT test samples for the selected drying salt
mgno3_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "MgNO3", 3)
mgno3_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "MgNO3", 1)

@@

```{r sporophyte-dt-NaCl, fig.height = 7, fig.width = 9.5, fig.cap = ""}
# Subset desiccation duration data
# H_polyanthos shows n=1, but this is only because pre/post were available for only one sample
# (actually had 8 samples total)
nacl_clusters_2013 <- 
  sporo_times %>%
  filter(str_detect(dataset, "2013")) %>%
  cluster_sporo_times("NaCl", 4) %>%
  mutate(
    serial_no = case_when(
      species %in% c("Didymoglossum_tahitense", "Crepidomanes_kurzii", "Callistopteris_apiifolia") & dry_time == "2" ~ "missing",
      species %in% c("Hymenophyllum_multifidum", "Hymenophyllum_digitatum") ~ "10140667",
      species %in% c("Hymenophyllum_polyanthos") ~ "10152774",
      species %in% c("Abrodictyum_dentatum") & dry_time == "2" ~ "missing",
      TRUE ~ "missing"
    ),
    serial_no = as.factor(serial_no)
  )

>>>>

---
title: ""
bibliography: 
  - references.bib
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-plant-research.csl"]
    includes:
      in_header: journal-of-plant-research-si.sty
# enable landscape mode selectively with pdflscape and newcommand 
# https://stackoverflow.com/questions/25849814/rstudio-rmarkdown-both-portrait-and-landscape-layout-in-a-single-pdf
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
  \usepackage{pdflscape}
  \newcommand{\blandscape}{\begin{landscape}}
  \newcommand{\elandscape}{\end{landscape}}
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

@@

```{r sporophyte-dt-LiCl, fig.height = 6.5, fig.width = 9, fig.cap = ""}
# Get mean times of each cluster of DT test samples for the selected drying salt
licl_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "LiCl", 3)
licl_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "LiCl", 1)

@@

```{r sporophyte-dt-MgNO3, fig.height = 6.5, fig.width = 9, fig.cap = ""}
# Get mean times of each cluster of DT test samples for the selected drying salt
mgno3_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "MgNO3", 3)
mgno3_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "MgNO3", 1)

@@

```{r sporophyte-dt-NaCl, fig.height = 6.5, fig.width = 9, fig.cap = ""}
# Subset desiccation duration data
# H_polyanthos shows n=1, but this is only because pre/post were available for only one sample
# (actually had 8 samples total)
nacl_clusters_2013 <- 
  sporo_times %>%
  filter(str_detect(dataset, "2013")) %>%
  cluster_sporo_times("NaCl", 4) %>%
  mutate(
    serial_no = case_when(
      species %in% c("Didymoglossum_tahitense", "Crepidomanes_kurzii", "Callistopteris_apiifolia") & dry_time == "2" ~ "missing",
      species %in% c("Hymenophyllum_multifidum", "Hymenophyllum_digitatum") ~ "10140667",
      species %in% c("Hymenophyllum_polyanthos") ~ "10152774",
      species %in% c("Abrodictyum_dentatum") & dry_time == "2" ~ "missing",
      TRUE ~ "missing"
    ),
    serial_no = as.factor(serial_no)
  )
